---
title: "Developing Data Products"
author: "Roman I Ozerov"
date: "August 4, 2017"
output: ioslides_presentation
---
Please use PgUp/PgDn to navigate the document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library (leaflet)
```

## NoVa flight schools

This document contains a map of flight schools in Nortern Virginia. By clicking on each map marker, you can see a web site of the appropriate flight school.
Note that some schools share the same airfield. You need to play with scale to see them all.

## Filght School listing

- Aviation Adventures LLC
- AV-ED Flight School
- Potomac Flight Training
- Atlantic Airways
- Dulles Aviation Inc
- Culpeper Regional Airport
- Sikorsky Aircraft Corporation (at Quantico)

## Map

```{r}
df <- data.frame(
  name = c("Aviation Adventures LLC", "AV-ED Flight School", "Potomac Flight Training", 
           "Atlantic Airways", "Dulles Aviation", "Culpeper Regional Airport", 
           "Sikorsky at Quantico"),
  pop = c("KJUO", "KJUO", "Simulator", "KJUO", "KHEF", "KCJR", "KNYG"),
  lat = c(39.077,39.077,38.590,39.077,38.721,38.525,38.503),
  lng = c(-77.557,-77.557,-77.250,-77.557,-77.515,-77.859,-77.305)
  )
sites <- c(
  "<a href = 'http://www.aviationadventures.com/'>Aviation Adventures LLC</a>",
  "<a href = 'http://www.av-ed.com/'>AV-ED Flight School</a>", 
  "<a href = 'http://www.potomacflighttraining.com/'>Potomac Flight Training</a>", 
  "<a href = 'http://www.atlantic-airways.com/'>Atlantic Airways</a>",
  "<a href = 'http://www.dullesaviation.com/'>Dulles Aviation Inc</a>",
  "<a href = 'http://www.culpeperairport.com/'>Culpeper Regional Airport</a>", 
  "<a href = 'http://www.lockheedmartin.com/us/what-we-do/aerospace-defense/sikorsky.html'>Sikorsky at Quantico</a>"
  ) 
df%>%
leaflet()%>%
addTiles()%>%
addMarkers(popup = sites, clusterOptions = markerClusterOptions())
```  
   